FinalManuscript_DISCS_UG

### 2019-03-04 parts/01_introduction_01contextofstudy.tex
Applied comments for chapter 1
Updated and cleaned up ch1

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel. Much research has been done on the development and application of various cryptosystems.

One particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.

 In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.

>>>>

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. Cryptosystems allow plaintexts, data which is commonly understood, to be encrypted as ciphertext, data which can only be understood by authorized parties using a key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel.

One particular application of cryptography is image encryption. While cryptosystems used to encrypt general digital data, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.

 Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting value secure. The result of the operations can be recovered when the data is decrypted.. In this manner, data is manipulated without compromising data privacy~\cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with general digital data, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. This study in particular focuses on facial recognition.
